---
title: "Cross reference in R Markdown"
author: "Young-geun Kim"
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Cross reference in R Markdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
output:
  rmarkdown::pdf_document:
    toc: yes
  rmarkdown::html_vignette:
    toc: yes
    fig_caption: yes
header-includes:
  - \usepackage{float}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "70%",
  fig.align = "center",
  fig.width = 6,
  fig.asp = .618,
  fig.pos = "H"
)
```

# Installation

```{r, eval=FALSE}
devtools::install_github("ygeunkim/rmdtool")
```

***

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
```

We generate simple data set.

```{r}
set.seed(1)
mydf <- tibble(x = rnorm(1000))
(mydf <-
  mydf %>% 
  mutate(y = 3 * x + rnorm(1000)))
```

***

# Cross referencing

Numbering equations, figures, and tables is a key factor in documentation. Referencing helps these numbers meaningful and useful both when writing and reading.

```{r}
library(rmdtool)
```

## Equation

At the beginning of the document, excecute `eqn_numbering()` with `results = 'asis'` if you want to use equation referencing in html document. This writes the script:

```
<script type="text/x-mathjax-config">
MathJax.Hub.Config({
  TeX: { equationNumbers: { autoNumber: "AMS" } }
});
</script>
```

```{r, echo=FALSE, results='asis'}
eqn_numbering()
```

\begin{equation} \label{eq:regression}
  y_i = \beta_0 + \beta_1 x_i + \epsilon_i
\end{equation}

Equation $\eqref{eq:regression}$ also works in html. See the Rmd file for the code.

## Figure caption

You will use `fig()` and `tab()`. To know how to use these function, you should see the [`rmd` file itself](https://github.com/ygeunkim/rmdtool/blob/master/vignettes/cross-ref.Rmd), not the rendered file.

### How to do

Look at the `fig.cap` option below.

````markdown
`r ''````{r scat, fig.cap = fig$cap("scat", "Scatter plot of the generated data")}
````

To reference above figure, write

```{r, echo=FALSE, comment=NA}
writeLines("$`r fig$ref(\"scat\")`$")
```

### Demo

```{r scat, fig.cap = fig$cap("scat", "Scatter plot of the generated data")}
mydf %>% 
  ggplot(aes(x, y)) +
  geom_point()
```

You can refer the above plot anywhere in the same file by $`r fig$ref("scat")`$

## Table caption

Similarly, `tab()` works for the table.

```{r dftable}
knitr::kable(head(mydf), caption = tab$cap("dftable", "Kable representation for tibble"))
```

To reference above table, write

```{r, echo=FALSE, comment=NA}
writeLines("$`r tab$ref(\"dftable\")`$")
```

Now you can refer the above table by $`r tab$ref("dftable")`$



